\documentclass{article}
\usepackage{textgreek}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{amssymb}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Assignment 4}
\author{Owen Bean}

\begin{document}
\maketitle


\section{Links}

Github: \href{https://github.com/owenbean400/NLPAssignment4}{https://github.com/owenbean400/NLPAssignment4}

\section{Step 1}

For P@1 value on stack exchange duplicate question with model "distilbert-base-nli-stsb-quora-ranking", I got 0.011. Looking at the data, I noticed the duplicate questions were the question itself, so I tried P@1 value, excluding same question ID guessed. That value was 0.156. This is concluding that the model is duplicating the same ID question, however, ignoring this factor has showed 15\% of the questions retrieved is correct duplicate question. The Mean reciprocal rank from 100 queries is 0.095. This shows the model is averaging the tenth question is correct duplicate.

\section{Step 2}

I've done fine-tuning to "distilbert-base-nli-stsb-quora-ranking" by the losses with 90\% of the data labeled as duplicate with another data label as not duplicate to train the new loss value on model. The results from 10\% testing data has P@1 value at 0.0118. I've tried the ignoring same question ID for P@1, which is 0.1417. The MRR value is 0.0931.

\section{Step 3}

I've used the same testing data for fine-tuning onto the pre-trained model. The P@1 scores were the same. The MRR score difference was 0.000658. The t-value is 7.2402. Looking at the T-table, 7.2402 is way off the table, making \(\alpha\) less than 0.0005. Therefore, there is no significant change from fine-tuning and pre-trained.

\end{document}